Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-08-22 Article.tex
Article update

\usepackage{gensymb}
\usepackage{accents}
\usepackage{xspace}
\usepackage{tabularx}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-5360-5121}

% Authors, for the paper (add full first names)
\Author{Pierre Tize Mha $^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------

%----------------------------------------------------------------------------------
\section{Materials and experiments\label{sec:MaterialsExperiments}}
%----------------------------------------------------------------------------------
The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
For further information, readers may refer to this other publication by our research team.
We will, however, list here-after the main points required to understand the proposed approach. \OP{Add a small introduction}

@@

The initial stress increase observed during deformation up to $\varepsilon=0.1$ is attributed to work hardening (WH).
Subsequently, from $\varepsilon=0.1$ to $0.2$, the flow stress demonstrates a continuous decline as the stress level increases until a peak or inflection point is reached, indicating the dominant influence of thermal softening surpassing work hardening.
At this stage, the stress-strain curve exhibits three different patterns as the strain increases: (i) gradual decrease to a steady state with DRV/DRX softening.
This pattern is observed for all deformation temperatures and strain rates ranging from $\mdot\varepsilon=0.001~\ps$ to $0.1~\ps$, except for those at $1050\celsius$ and $1100\celsius$; (ii) higher stress levels without significant softening and work hardening at $1050\celsius$ and $1100\celsius$ with a strain rate of $0.1~\ps$; (iii) continuous increase with significant work hardening observed for all deformation temperatures and a strain rate of $1~\ps$.
This suggests that softening due to DRX (dynamic recrystallization) occurs at high temperatures and low strain rates.
In contrast, at higher strain rates and lower temperatures, the rate of softening due to DRX is slowed down by higher work hardening rates.
As a result, both the peak stress $\sigma_p$ and the onset of steady-state flow occur at higher strain levels.
The drop in stress observed at all temperatures and strain rates of $\mdot\varepsilon=0.001-5.0~\ps$ is due to the occurrence of DRX.

Dynamic recrystallization is an important phenomenon for controlling the microstructural and mechanical properties of a material during hot working.
In some materials, such as aluminum, dynamic recrystallization can balance work hardening, resulting in the rapid appearance of a plateau.
However, in many austenitic steels, the kinetics of restoration are weak and, as a result, dynamic recrystallization can be triggered at a critical condition of strain accumulation.
Because of the significant influence of dynamic recrystallization on the material's flow stress at high temperature, this inevitably affects the material's microstructure after hot working, and prediction of the critical conditions for the onset of dynamic recrystallization is therefore crucial to good material characterization.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation and the deformation parameters (deformation rate, temperature and deformation) condition dynamic recrystallization, which can only be triggered if the critical deformation is reached, and this deformation can be determined using metallography.
However, this technique requires extensive sampling before and after critical deformation.
In addition, phase changes during cooling from the hot working temperature modify the deformed structure, making metallographic analysis difficult.
Hence the need for simpler techniques, such as the development of analytical models.
With this in mind, a number of studies have been carried out to determine analytically the initiation of dynamic recrystallization.

In this paper we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to compute the evolution of DRX of the material during the deformation.
The raw data acquired from the Gleeble thermosimulator will subsequently be used to identify the material flow law and the parameters of the DRX model.

@@

In this Section we will determine the critical deformation required to initiate recrystallization.
Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the first to study this phenomenon, observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$ and attributed to this inflection point the start of dynamic recrystallization and therefore the critical values $\varepsilon_c$ and $\sigma_c$ of the strain and the stress respectively.
Later Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} further demonstrated that this inflection point is associated with a thermodynamic free energy released during dislocation motion, and consequently endorse the dynamic recrystallization hypothesis describing this inflection point.
Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used today, to determine the critical conditions for the initiation of dynamic recrystallization.
In their approach, a polynomial of $3^\text{th}$ degree is adopted to describe the shape of the curve $\theta(\sigma)$ and, using the second derivative, they manage to identify the critical stress and strain ($\sigma_c$ and $\varepsilon_c$).

@@

%----------------------------------------------------------------------------------
\subsubsection{ANN based filtering method for raw data\label{subsec:ANNbasics}}
%----------------------------------------------------------------------------------
In order to improve the results obtained from the critical value identification procedure, we propose here to use the universal approximator capability of artificial neural networks to replace each strain-hardening curve by its representation in the form of an ANN with 1 input (strain) and 1 output (stress).
In such a network, each layer of neurons is connected to the one before it and the one after it by weighted connections.
Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

No activation function was used for the output neuron of the ANN as usually done in a regression application.
The architecture chosen for our application corresponds to 2 hidden layers of 7 and 5 neurons respectively, as illustrated in Figure \ref{fig:ANN-7-5}.
If $n$ and $m$ are the number of neurons of the first and second hidden layers respectively, the number of internal parameters $N_{int}$ of the model is given by $N_{int}=m(2+n)+2n+1$.
So that for a $7-5$ network, $N_{int}=60$.
\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:ANN-7-5}
\end{figure}
The Python program used for training the neural network was developed using the specialized Python library, Tensorflow \cite{Abadi-2016}.
The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.

%----------------------------------------------------------------------------------
\subsubsection{ANN filtering results and DRX model parameters evaluation\label{subsec:ANNapplication}}
%----------------------------------------------------------------------------------
Since the DRX occurs only for the 4 strain rates within the range $[0.001~\ps-1.0~\ps]$, we will only use the first 20 stress/strain curves for the DRX critical parameters' identification.
Each of the 20 curves, made up of 701 couples of strain-stress values, was processed independently by a neural network, leading to 20 identified architectures.
As an example, Figure \ref{fig:AnnFit} shows the experimental values of the stress/strain curve for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$ (blue line) and the results from the neural network identified from these data (red line).
\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:AnnFit}
\end{figure}
The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the mean absolute relative error ($\MARE$) defined by Equation (\ref{eq:AARE}):
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the root-mean-squared error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and $N$ is the total number of data points used to compute those coefficients.
For the proposed ANN filter $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a $11^{th}$ order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:AnnTheta}
\end{figure}

%\begin{table}[H]
%\caption{Architecture and accuracy coefficients for all the proposed networks.}
%\newcolumntype{C}{>{\centering\arraybackslash}X}
%\newcolumntype{L}{>{\raggedright\arraybackslash}X}
%\begin{tabularx}{\textwidth}{LCCCCCC}
%\hline
%Coefficient & $\mdot\varepsilon$ & $1050\celsius$ & $1100\celsius$ & $1150\celsius$ & $1200\celsius$ & $1250\celsius$  \\
%\hline
%$\MARE(\%)$ & $0.001$ & $0.231$ & $1.13$ & $1.05$ & $1.08$ & $0.75$ \\
%$\RMSE(\MPa)$ & $0.001$ & $0.093$ & $0.59$ & $0.57$ & $0.65$ & $0.46$ \\
%\hline
%\end{tabularx}
%\label{tab:Errors}
%\end{table}

%----------------------------------------------------------------------------------
\section{Numerical simulation of the compression\label{sec:NumSim}}
%----------------------------------------------------------------------------------

%----------------------------------------------------------------------------------
\subsection{Identification of the ANN constitutive law\label{subsec:ANNConstitutiveLaw}}
%----------------------------------------------------------------------------------
In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
The model can therefore be described as an elastoplastic model with the influence of strain rate and temperature.
This type of behavior generally leads to Johnson-Cook \cite{Johnson-1983}, Zerilli Armstrong \cite{Zerilli-1987}, Hansel Spittle \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
As reported by Tize Mha \eal \cite{TizeMha-2023}, Johnson-Cook, Zerilli Armstrong or Hansel Spittle type models, while providing a more or less faithful reproduction of material behavior at strain rates above $1~\ps$, do not take into account the softening due to dynamic recrystallization visible on experimental curves for strain rates below $1~\ps$ as reported in Figure  \ref{fig:RawData}.
Indeed, for the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ up to a value of around $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
Only the Arrhenius model can more or less account for this softening at low strain rates.
As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
Correctly defining the hyperparameters of this neural network (number of hidden layers, number of neurons, activation functions, etc.) allows us to obtain a flow law that faithfully reproduces the data obtained from compression tests.

>>>>

\usepackage{gensymb}
\usepackage{accents}
\usepackage{xspace}
\usepackage{tabularx}
\usepackage{lscape}
\usepackage{comment}
\usepackage{inputenc}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application}

%\Title{Artificial neural network based critical conditions for dynamic recrystallization initiation of medium carbon steel  and Application : Analytical and Finite Element Modeling}%

% MDPI internal command: Title for citation in the left column
\TitleCitation{Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-5360-5121}% Add \orcidB{} behind the
%author's name
\newcommand{\orcidauthorD}{0000-0002-0815-1984}

% Authors, for the paper (add full first names)
\Author{Pierre Tize Mha $^{1}$\orcidD{}, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{\textcolor{red}{The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.}}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Dynamic recrystallization (DRX) is a process that occurs in certain materials, especially in metals and alloys, when they undergo plastic deformation (deformation that is not reversible). It is a phenomenon commonly observed during hot working processes like hot rolling, hot forging, or hot extrusion. When a metal or alloy is subjected to high temperatures and significant plastic deformation, the existing grain structure is broken down, and new, smaller grains form in its place and this phenomenon is called DRX. It is different from static recrystallization, which occurs at lower temperatures and takes longer to form new grains. The process of DRX is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures. DRX offers several advantages during hot working processes in the sense that it helps in refining the grain size, which enhances the mechanical properties of the material, such as strength and toughness. Additionally, it reduces the overall strain energy, which can lead to a more uniform microstructure and improved material properties.

It is well known that during hot deformation with a relatively high strain rate, the dislocation density increases while dynamic recovery (DRC) tries to diminish the density. If the rate of dislocation density increase is greater than can be accommodated by DRC, DRX is initiated at a certain point. This applies particularly to low and medium stacking fault energy for fcc metals. Therefore, mastery of critical conditions for DRX is of considerable interest for the modeling of industrial processes but the extent of DRX depends on several factors, including the material's composition, deformation temperature, strain rate, and the degree of deformation. It is an essential phenomenon to be taken into account and controlled in industrial processes where hot working is employed to shape metals and alloys into various products. By optimizing the parameters, engineers can achieve desired microstructures and mechanical properties in the final product. Several researchers have proposed various techniques to determine DRX's critical conditions such as metallography. However, this technique requires extensive sampling before and after the critical deformation. Additionally, phase changes during cooling from the hot working temperature alter the deformed structure, making metallographic analysis challenging. Hence, there is a need to resort to other simpler techniques, such as the development of analytical models. In this context, several studies have been conducted to analytically determine the initiation of DRX. For example, Barnett \eal \cite{barnett2000predicting} have identified the critical strain for initiation of DRX using the kinetics of static recrystallization (SRX) modified to allow SRX to begin before the end of deformation. This approach defines the critical stress for the initiation of SRX during deformation. On the basis of a dislocation density work hardening model, Gottstein \eal \cite{gottstein2004prediction} have also predicted the critical strain for initiation of DRX. The onset of DRX can also be identified phenomenologically from the inflection point in the strain hardening rate $\theta=\frac{\partial \sigma}{\partial \varepsilon} = f(\sigma)$ whose understanding is crucial in materials processing and design..

The DRX phenomenon based on inflection point was first studied by Ryan and McQueen \cite{ryan1989dynamic,ryan1990dynamic,ryan1990flow}, who observed the appearance of an inflection point on the curve $\theta=f(\sigma)$ before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this inflection point. Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} further demonstrated that this inflection point is associated with the thermodynamic energy released during the movement of dislocations, thus confirming the hypothesis of DRX describing this inflection point; this signifies that an additional softening mechanism begins to operate (in addition to DRC). Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used nowadays, to determine the critical conditions for the initiation of DRX. In their approach, they adopted a third-degree polynomial to describe the shape of the curve $\theta=f(\sigma)$ and, by using the second derivative, they identified the critical strain $\varepsilon_c$ and stress $\sigma_c$. Once the critical conditions are calculated, they are considered as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}, which is widely used to estimate the volumic fraction of DRX ($X_{drx}$) during hot working. Li \eal \cite{li2015experimental} explored the DRX characteristics of micro-alloyed plastic molding steel, using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to identify all key parameters. Zhang \eal \cite{zhang2016kinetics} studied the DRX behaviors of medium carbon CreNieMo steel alloy using the Avrami kinetics model equation, and qualitatively characterized the metallurgical properties as a function of the Zener-Hollomon parameter. Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} predicted the microstructural evolution of Mn alloy (with an emphasis on the DRX and grain growth phenomena) using this well-known model and found that the predicted microstructures were consistent with those revealed by multiple compression tests. The same equation was used by Wan \eal \cite{wan2017experimental} to predict the microstructural evolution of TiAl-based alloys during hot compression. Li \eal \cite{li2018finite} verified the reliability of the Avrami kinetics model equation during compression testing of Inconel 718 bolts. Cui \eal \cite{cui2016hot} investigated DRX using the Avrami
kinetics model equation and showed that the evolution of a $\beta$-solidifying TiAl alloy commonly began at triangular boundaries and only later affected the lamellae.

The accuracy of the critical conditions for DRX is strongly related to how the curve $\theta=f(\sigma)$ is obtained. Indeed, the direct use of raw data from experiments does not provide usable curves. Therefore, commonly used methods involve either smoothing the curve $\sigma=f(\varepsilon)$  as much as possible or approximating this curve with a polynomial function that can reproduce it and deducing the curve $\theta=f(\sigma)$ from it. The disadvantage of these two methods is that they do not always guarantee a good smoothing of the curve $\sigma=f(\varepsilon)$. However, an Artifical Neural Networks (ANN) method is a universal approximator that has proven its effectiveness in several fields, including predicting the material's flow behavior. Based on this tool, we propose, in this study, to replace the two smoothing methods with an ANN to obtain the critical conditions for DRX. In other words, the proposed approach suggests using an ANN to model the relationship between the stress ($\sigma$) and the rate hardening ($\theta$) directly, avoiding the need for explicit smoothing of experimental data. By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX. \textcolor{red}{Using ANN in materials science and engineering has gained popularity due to their ability to learn complex patterns and relationships from data, making them valuable tools for various predictions and analyses in the field. By leveraging a ANN in this context, researchers aim to improve the accuracy and reliability of predictions related to DRX behavior in materials during deformation}.

%----------------------------------------------------------------------------------
\section{Materials and experiments\label{sec:MaterialsExperiments}}
%----------------------------------------------------------------------------------
The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
For further information, readers may refer to this other publication by our research group. We will, however, list here-after the main points required to understand the proposed approach. The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted. At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing. In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction. It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.\OP{Already done}

@@

The initial stress increase observed during deformation up to $\varepsilon=0.1$ is attributed to work hardening (WH).
Subsequently, from $\varepsilon=0.1$ to $0.2$, the flow stress demonstrates a continuous decline as the stress level increases until a peak or inflection point is reached, indicating the dominant influence of thermal softening surpassing work hardening.
At this stage, the stress-strain curve exhibits three different patterns as the strain increases: (i) gradual decrease to a steady state with DRV/DRX softening.
This pattern is observed for all deformation temperatures and strain rates ranging from $\mdot\varepsilon=0.001~\ps$ to $0.1~\ps$, except for those at $1050\celsius$ and $1100\celsius$; (ii) higher stress levels without significant softening and work hardening at $1050\celsius$ and $1100\celsius$ with a strain rate of $0.1~\ps$; (iii) continuous increase with significant work hardening observed for all deformation temperatures and a strain rate of $1~\ps$.
This suggests that softening due to DRX  occurs at high temperatures and low strain rates.
In contrast, at higher strain rates and lower temperatures, the rate of softening due to DRX is slowed down by higher work hardening rates.
As a result, both the peak stress $\sigma_p$ and the onset of steady-state flow occur at higher strain levels.
The drop in stress observed at all temperatures and strain rates of $\mdot\varepsilon=0.001-5.0~\ps$ is due to the occurrence of DRX.

DRX is an important phenomenon for controlling the microstructural and mechanical properties of a material during hot working.
In some materials, such as aluminum, DRX can balance work hardening, resulting in the rapid appearance of a plateau.
However, in many austenitic steels, the kinetics of restoration are weak and, as a result, DRX can be triggered at a critical condition of strain accumulation.
Because of the significant influence of DRX on the material's flow stress at high temperature, this inevitably affects the material's microstructure after hot working, and prediction of the critical conditions for the onset of DRX is therefore crucial to good material characterization.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation and the deformation parameters (deformation rate, temperature and deformation) condition DRX, which can only be triggered if the critical deformation is reached, and this deformation can be determined using metallography.
However, this technique requires extensive sampling before and after critical deformation.
In addition, phase changes during cooling from the hot working temperature modify the deformed structure, making metallographic analysis difficult.
Hence the need for simpler techniques, such as the development of analytical models.
With this in mind, a number of studies have been carried out to determine analytically the initiation of DRX.

In this paper we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to compute the evolution of DRX of the material during the deformation. The raw data acquired from the Gleeble thermosimulator will subsequently be used to identify the material flow law and the parameters of the DRX model. The parameters of JMAK model are obtained through a two-step process. Firstly, the critical stresses and strains are determined, where the ANN model is utilized to obtain well-filtered curves. Secondly, these critical values are employed as input data for the calculation of parameters in the JMAK model, aiming to predict the volume fraction of dynamic recrystallization.

@@

In this Section we will determine the critical deformation required to initiate recrystallization.
Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the first to study this phenomenon, observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$ and attributed to this inflection point the start of DRX and therefore the critical values $\varepsilon_c$ and $\sigma_c$ of the strain and the stress respectively.
Later Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} further demonstrated that this inflection point is associated with a thermodynamic free energy released during dislocation motion, and consequently endorse the DRX hypothesis describing this inflection point.
Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used today, to determine the critical conditions for the initiation of DRX.
In their approach, a polynomial of $3^\text{th}$ degree is adopted to describe the shape of the curve $\theta(\sigma)$ and, using the second derivative, they manage to identify the critical stress and strain ($\sigma_c$ and $\varepsilon_c$).

@@

%----------------------------------------------------------------------------------
\subsubsection{ANN based filtering model's archicture \label{subsec:ANNbasics}}
%----------------------------------------------------------------------------------
In order to improve the results obtained from the critical value identification procedure, we propose here to use the universal approximator capability of artificial neural networks to replace each strain-hardening curve by its representation in the form of an ANN with 1 input (strain) and 1 output (stress).
In such a network, each layer of neurons is connected to the one before it and the one after it by weighted connections.
Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

No activation function was used for the output neuron of the ANN as usually done in a regression application.
The architecture chosen for our application corresponds to 2 hidden layers of 7 and 5 neurons respectively, as illustrated in Figure \ref{fig:ANN-7-5}.
If $n$ and $m$ are the number of neurons of the first and second hidden layers respectively, the number of internal parameters $N_{int}$ of the model is given by $N_{int}=m(2+n)+2n+1$.
So that for a $7-5$ network, $N_{int}=60$.
\begin{figure}[H]
%\centering
\includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:ANN-7-5}
\end{figure}
The Python program used for training the neural network was developed using the specialized Python library, Tensorflow \cite{Abadi-2016}.
The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.

%----------------------------------------------------------------------------------
\subsubsection{ANN filtering based model's application \label{subsec:ANNapplication}}
%----------------------------------------------------------------------------------
Since the DRX occurs only for the 4 strain rates within the range $[0.001~\ps-1.0~\ps]$, we will only use the first 20 stress/strain curves for the DRX critical parameters' identification.
Each of the 20 curves, made up of 701 couples of strain-stress values, was processed independently by a neural network, leading to 20 identified architectures.
As an example, Figure \ref{fig:AnnFit} shows the experimental values of the stress/strain curve for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$ (blue line) and the results from the neural network identified from these data (red line).
\begin{figure}[H]
%\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:AnnFit}
\end{figure}
The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the mean absolute relative error ($\MARE$) defined by Equation (\ref{eq:AARE}):
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the root-mean-squared error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and $N$ is the total number of data points used to compute those coefficients.
For the proposed ANN filter $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a $11^{th}$ order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.

It can clearly be observed that using the ANN model to describe the $\sigma=f(\varepsilon)$ curve is better than using a $11^{th}$ order polynomial fit, as evidenced by the lower estimated error. Therefore, this architecture of the ANN model is employed for the remaining curves, leading directly to deduce the hardening $\theta=f(\sigma)$ curves, which represent the rate of change of stress with respect to strain ($\frac{\partial \sigma}{\partial \varepsilon}$). An example of computing the hardening curve for one temperature is given on Figure \ref{fig:AnnTheta} and for remaining temperatures, Figure \ref{fig:nThetaOP} can give an overview. The same procedure is used for the four initial strain rates. These curves provide essential information about critical stresses and strains needed for predicting DRX in the subsequent analysis.

\begin{figure}[H]
%\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
\caption{An example of computing hardening curve based on ANN model.}
\label{fig:AnnTheta}
\end{figure}

\begin{figure}[H]
%\centering
\includegraphics[width=0.99\columnwidth]{Figures/nThetaOP}
\caption{Work hardening computation for $1$ strain rate and $5$ temperatures.}
\label{fig:nThetaOP}
\end{figure}

%----------------------------------------------------------------------------------
\subsubsection{Critical conditions evaluation\label{subsec:CrConditions}}
%----------------------------------------------------------------------------------
As mentioned in the previous section, dynamic recrystallization initiates if and only if a certain critical condition level is reached. Determining these critical conditions remains challenging, as it requires the development of models capable of calculating the corresponding critical stress and strain. Thus, the Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} method, widely recognized today, will be employed in this study. The method involves using a third-degree polynomial function to describe the functions $\theta(\sigma)$ and $\ln \theta(\varepsilon)$curves as shown in Figure \ref{fig:fThetaOP} , with the purpose of identifying the inflection points corresponding to critical stress $\sigma_c$ and critical strain $\varepsilon_c$. Also from those curves, peak stress $\sigma_p$ and peak strain $\varepsilon_p$ can be deduced. The Poliak and  Jonas model \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} is given as follow:
\begin{equation}
\theta = A\sigma^3 + B\sigma^2 + C\sigma + D
\end{equation}
Where $A, B, C,$ and $D$ are constants specific to a given deformation condition. The inflection point of a function is determined by setting the second derivative of that function to zero and the following equation is obtained:
\begin{equation}
\frac{d^2 \theta}{d \sigma^2} = 6A\sigma + 2B
\end{equation}
Therefore, the critical stress for the initiation of DRX is obtained as follows:
\begin{equation}
6A\sigma_c + 2B = 0 \Longrightarrow \sigma_c = -B/3A
\end{equation}
Similarly, the critical strain is calculated using the following equations:
\begin{equation}
\ln \theta = A_1\varepsilon^3 + B_1\varepsilon^2 + C_1\varepsilon + D_1 
\end{equation}
\begin{equation}
\frac{d^2 \ln \theta}{d \varepsilon^2} = 6\varepsilon A_1 + 2B_1 ~~\text{and} ~~\frac{d^2 \ln \theta}{d \varepsilon^2}= 0 \Longrightarrow \varepsilon_c = -B_1/3A_1
\end{equation}
Applying the same method to the first four strain rates and all temperatures, the critical stress and strain, peak stress and peak strain are summarised in the Table \ref{tab:OPparams}. Once the critical conditions of the DRX are known, therefore they can be used as input to deduce the volume fraction of the DRX, which will be the subject of the next section.
\begin{figure}[H]
%\centering
\includegraphics[width=0.99\columnwidth]{Figures/fThetaOP}
\caption{Work hardening polynomial fiting based on Poliak and Jonas  model  \cite{najafizadeh2006predicting}.}
\label{fig:fThetaOP}
\end{figure}
